Displacement of fishing effort by Large Scale Marine Protected Areas

### 2018-10-11 rmd/Manuscript.Rmd
Updated effort data

```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels. Vertical dashed line indicates PIPA closure."}
effort_by_vessel %>% 
  filter(baci_strict) %>%
  group_by(year, gear, treated, post, month) %>% 
  summarize(total_hours = sum(hours),
            mean_hours = mean(hours),
            n_mmsi = n()) %>% 
  ungroup() %>% 
  mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
  select(-year) %>% 
  gather(variable, value, -c(date, month, post, gear, treated)) %>% 
  ggplot(aes(x = date, y = value, color = treated)) +
  geom_line() +
  geom_point() +
  facet_wrap(gear~variable, scales = "free", ncol = 3) +
  ggtheme_plot() +
  scale_color_brewer(palette = "Set1") +
  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
```

@@

model_data <- effort_by_vessel %>% 
  filter(baci_strict,
         gear == "purse_seines") %>% 
  mutate(post = post * 1,
         treated = treated * 1,
         year2 = year^2,
         mmsi_c = as.factor(mmsi))

stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     t.auto = T,
                     p.auto = T,
                     type = "latex",
                     omit = c("flag", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Flag FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "\\label{tab:purse}Fishing hours from GFW for purse seiners (n = 106; 38 control, 68 treatment). Asterisks indicate significance levels. Numbers in parenthesis represent heteroskedastic-robust standard errors.")
```

>>>>

```{r, echo = F, fig.cap = "\\label{fig:all_vessels}Fishing hours and number of vessels by month for all vessels. Vertical dashed line indicates PIPA closure."}
effort_by_vessel %>% 
  filter(baci_strict) %>%
  group_by(year, gear, treated, post, month, date) %>% 
  summarize(total_hours = sum(hours),
            mean_hours = mean(hours),
            n_mmsi = n()) %>% 
  ungroup() %>% 
  # mutate(date = lubridate::date(paste(year, month, "01", sep = "/"))) %>% 
  select(-year) %>% 
  gather(variable, value, -c(date, month, post, gear, treated)) %>% 
  ggplot(aes(x = date, y = value, color = treated)) +
  geom_line() +
  geom_point() +
  facet_wrap(gear~variable, scales = "free", ncol = 3) +
  ggtheme_plot() +
  scale_color_brewer(palette = "Set1") +
  geom_vline(xintercept = lubridate::date(paste(2015, 01, "01", sep = "/")), linetype = "dashed")
```

@@

model_data1 <- effort_by_vessel %>% 
  filter(baci_strict,
         gear == "purse_seines") %>% 
  mutate(post = post * 1,
         treated = treated * 1,
         year_month_c = as.character(year_month),
         quarter_c = as.character(quarter))

model_data2 <- effort_by_vessel %>% 
  filter(baci_strict,
         gear == "purse_seines",
         experiment1) %>% 
  mutate(post = post * 1,
         treated = treated * 1,
         year_month_c = as.character(year_month),
         quarter_c = as.character(quarter))

model_data3 <- effort_by_vessel %>% 
  filter(baci_strict,
         gear == "purse_seines",
         experiment2) %>% 
  mutate(post = post * 1,
         treated = treated * 1,
         year_month_c = as.character(year_month),
         quarter_c = as.character(quarter))

model_data4 <- effort_by_vessel %>% 
  filter(baci_strict,
         gear == "purse_seines",
         experiment3) %>% 
  mutate(post = post * 1,
         treated = treated * 1,
         year_month_c = as.character(year_month),
         quarter_c = as.character(quarter))

m1.1 <- lm(hours ~ post*treated, data = model_data1)
m2.1 <- lm(hours ~ year_month_c*treated, data = model_data1)
m3.1 <- lm(hours ~ quarter_c*treated, data = model_data1)

m1.2 <- lm(hours ~ post*treated, data = model_data2)
m2.2 <- lm(hours ~ year_month_c*treated, data = model_data2)
m3.2 <- lm(hours ~ quarter_c*treated, data = model_data2)

m1.3 <- lm(hours ~ post*treated, data = model_data3)
m2.3 <- lm(hours ~ year_month_c*treated, data = model_data3)
m3.3 <- lm(hours ~ quarter_c*treated, data = model_data3)

m1.4 <- lm(hours ~ post*treated, data = model_data4)
m2.4 <- lm(hours ~ year_month_c*treated, data = model_data4)
m3.4 <- lm(hours ~ quarter_c*treated, data = model_data4)

models <- list(m1.1, m1.2, m1.3, m1.4)

stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     t.auto = T,
                     p.auto = T,
                     type = "latex",
                     omit = c("flag", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Flag FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "DiD",
                     out = "DID.html")

models <- list(m2.1, m2.2, m2.3, m2.4)
stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     t.auto = T,
                     p.auto = T,
                     type = "latex",
                     omit = c("flag", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Flag FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "DiD - months",
                     out = "months.html")

models <- list(m3.1, m2.2, m3.3, m3.4)
stargazer::stargazer(models,
                     se = commarobust::makerobustseslist(models),
                     t.auto = T,
                     p.auto = T,
                     type = "latex",
                     omit = c("flag", "month"),
                     add.lines = list(c("Month FE", "No", "Yes", "Yes", "Yes"),
                                      c("Flag FE", "No", "No", "No", "Yes")),
                     omit.stat = c("adj.rsq", "f", "ser"),
                     header = F,
                     title = "DiD - quarters",
                     out = "quarters.html")
```
